### 2023-03-05 manuscript.tex
Update 03.use-cases-a.md [ci skip]
This build is based on
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6855a7f181d90025efefe38a357366e9594bb35d.

This commit was created by the following CI build and job:
https://github.com/SORTEE-Github-Hackathon/manuscript/commit/6855a7f181d90025efefe38a357366e9594bb35d/checks
https://github.com/SORTEE-Github-Hackathon/manuscript/actions/runs/4333432537

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/3601d15cc9a4fffce47dacf71ccee802a971eb55/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/3601d15cc9a4fffce47dacf71ccee802a971eb55}{SORTEE-Github-Hackathon/manuscript@3601d15}
on 2023-03-04.

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects'' (\protect\hyperlink{definitions}{Box 1}).
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects provides users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution (\protect\hyperlink{ref-3UAritXO}{\emph{Issues · Fmsabatini/sPlotOpen\_Manuscript}, n.d.}, =is\%3Aissue+is\%3Aclosed; \emph{e.g.}, see issues and discussions in the sPlotOpen manuscript repository, \protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}).
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
However, one can opt to receive new issues, discussions, and responses as emails and can post replies by email as well.\\
This allows for centralized communication for a team even when some members prefer to use email for communication.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).

@@

\leavevmode\vadjust pre{\hypertarget{ref-3UAritXO}{}}%
\emph{Issues · fmsabatini/sPlotOpen\_Manuscript}. (n.d.). GitHub. Retrieved March 4, 2023, from \url{https://github.com/fmsabatini/sPlotOpen_Manuscript}

>>>>

This manuscript
(\href{https://SORTEE-Github-Hackathon.github.io/manuscript/v/6855a7f181d90025efefe38a357366e9594bb35d/}{permalink})
was automatically generated
from \href{https://github.com/SORTEE-Github-Hackathon/manuscript/tree/6855a7f181d90025efefe38a357366e9594bb35d}{SORTEE-Github-Hackathon/manuscript@6855a7f}
on 2023-03-05.

@@

Modern research in ecology and evolution is highly collaborative, bringing together multidisciplinary teams from various institutions (\protect\hyperlink{ref-1HhzKAC1K}{Goring et al., 2014}).
On GitHub, collaborators can share feedback, brainstorm ideas, and troubleshoot problems (Figure \ref{fig:github-diagram}).
Project management can happen via three GitHub repository features: ``Issues'', ``Discussion'' and ``Projects'' (\protect\hyperlink{definitions}{Box 1}).
Github Issues allow for discrete tasks and sub-tasks to be identified, assigned to team members, and categorized with custom labels.
Github Discussions serve as a message board for conversation.
Finally, GitHub Projects provides users with real-time tracking of project priorities and status (\protect\hyperlink{ref-RhBKe0MG}{\emph{About Projects}, n.d.}).
For instance, one can create a discussion on a project repository to decide which method to apply for biodiversity data analysis.
Then, an issue can be created to establish steps and responsibilities including data formatting, statistical analyses, figure generation, and issue resolution.
For example, sPlotOpen (\protect\hyperlink{ref-doi:10.1111ux2fgeb.13346}{\textbf{doi:10.1111/geb.13346?}}) manuscript repository contains issues and discussions tracking the development of the project (see \url{https://github.com/fmsabatini/sPlotOpen_Manuscript/issues?q=is\%3Aissue+is\%3Aclosed}).
Using GitHub for all project-related conversation and planning, rather than email or messaging tools, makes it easier to keep track of progress throughout the lifespan of a project.
However, one can opt to receive new issues, discussions, and responses as emails and can post replies by email as well.
This allows for centralized communication for a team even when some members prefer to use email for communication.
Unlike emails and messages which can get lost as more new tasks arise, GitHub issues are intentionally closed by repository administrators hiding the issue from view (closed issues remain accessible but not immediately visible).

@@
